\input{doc-class-cours.tex}

\begin{document}

Welcome to Introduction to Applied Cryptography.  Cryptography is an essential component of cybersecurity. The need to protect sensitive information and ensure the integrity of industrial control processes has placed a premium on cybersecurity skills in today’s information technology market.  Demand for cybersecurity jobs is expected to rise 6 million globally by 2019, with a projected shortfall of 1.5 million, according to Symantec, the world’s largest security software vendor. According to Forbes, the cybersecurity market is expected to grow from \$75 billion in 2015 to \$170 billion by 2020. In this specialization, you will learn basic security issues in computer communications, classical cryptographic algorithms, symmetric-key cryptography, public-key cryptography, authentication, and digital signatures. These topics should prove especially useful to you if you are new to cybersecurity Course 1, Classical Cryptosystems, introduces you to basic concepts and terminology related to cryptography and cryptanalysis. It is recommended that you have a basic knowledge of computer science and basic math skills such as algebra and probability.





\section*{Semaine 1 - The insides of giant planets (week 1)}


\begin{itemize}[label={$\bullet$}]
    \item Vidéo : 2.01: Introduction to Jupiter
    \item Vidéo : 2.02: Measuring density
    \item Demande de discussion : Transit of Venus!
    \item Vidéo : 2.03: Using density
    \item Vidéo : 2.04: Hydrostatic equilibrium
    \item Vidéo : 2.05: Hydrogen equation of state
    \item Vidéo : 2.06: Heat transport
    \item Vidéo : 2.07: Theoretical internal structure
    \item Vidéo : 2.08: A core from gravity ?
    \item Vidéo : 2.09: Magnetic fields
    \item Vidéo : 2.10: The upper atmosphere and the Galileo probe
    \item Vidéo :2.11: Picture models
\end{itemize}


\end{document}